---
title: "introduction-to-KrakenR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction-to-KrakenR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(KrakenR)
```

## Introduction

The KrakenR package provides a user-friendly interface to the Kraken cryptocurrency exchange's REST API. It allows R users to access real-time and historical market data, asset information, and exchange metrics, making it a valuable tool for financial analysts, traders, and researchers interested in the cryptocurrency markets.

This vignette will introduce key functionalities of the package, showcasing how to use the API functions to retrieve market data and more.

## Installation

You can install KrakenR directly from GitHub:

```{r install_load, eval=FALSE}
# Install the development version from GitHub
devtools::install_github("nathanael-g-durst/KrakenR")

# Load the package
library(KrakenR)

```

## Overview of Available Functions

The package includes several key functions that allow users to fetch various types of data from the Kraken exchange:

  * `getAssets()` - Retrieve detailed asset information.
  * `getOB()` - Fetch order book data for a specific trading pair.
  * `getOHLC()` - Access OHLC (Open, High, Low, Close) data for a trading pair.
  * `getPairs()` - Retrieve tradable asset pair information.
  * `getSpreads()` - Fetch recent spread data.
  * `getStatus()` - Get the current system status of the Kraken exchange.
  * `getTickers()` - Retrieve detailed ticker information for trading pairs.
  * `getTime()` - Fetch the current Kraken server time.
  * `getTrades()` - Retrieve recent trade data for a trading pair.

## Example Workflow

This section provides a detailed walkthrough using KrakenR to access Kraken market data.

### 1. Fetching Asset Information

To retrieve detailed information about all available assets or specific ones:
```{r fetching_asset_information}
# Fetch all available assets
assets_all <- getAssets()

# Fetch data for specific assets
assets_specific <- getAssets(c("BTC", "ETH", "ADA"))

```

The getAssets() function returns a data frame containing asset information, such as the asset class, decimals, and status.

```{r fetching_asset_information_example, echo=FALSE}
# Preview of asset information
knitr::kable(head(assets_all))

```

### 2. Retrieving Order Book Data

You can use `getOB()` to fetch order book data for a specific trading pair:

```{r retrieving_order_book_data}
# Fetch order book data for ADAEUR pair
order_book <- getOB("ADAEUR")

# Fetch order book data with a limit on the number of orders
order_book_limited <- getOB("ADAEUR", count = 3)

```

The output includes bid and ask orders, sorted by price, and can be used for market analysis.

```{r retrieving_order_book_data_example, echo=FALSE}
# Preview of asset information
knitr::kable(head(order_book_limited))

```
